\documentclass[]{deedy-resume-openfont}

\begin{document}

\hyphenation{knowledge working edinburgh technology experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Leon}{Overweel}{
    \href{https://leonoverweel.com}{leonoverweel.com} \ | \
    \href{mailto:l.overweel@gmail.com}{l.overweel@gmail.com} \ | \
    \href{tel:+31612159303}{+31 6 1215 9303}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.32\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection{University of Edinburgh}
\descript{MSc Artificial Intelligence}
\location{Sep. 2018 - Aug. 2019 | Edinburgh, UK}

\vspace{0.4\topsep}
Coursework: \begin{small}(Semesters 1 + 2 completed)
\vspace{0.2\topsep}

\custombold{Semester 1:}
Machine Learning and Pattern Recognition \textbullet \
Extreme Computing \textbullet \
Social and Technological Networks \textbullet \
Inf. Research Review \textbullet \
ML Practical
\vspace{0.3\topsep}

\custombold{Semester 2:}
Reinforcement Learning \textbullet \
Natural Language Understanding, Generation, and Machine Translation \textbullet \
Innovation-driven Entrepreneurship \textbullet \
Inf. Project Proposal \textbullet \
ML Practical (cont.)
\vspace{0.3\topsep}

\custombold{Summer - MSc Thesis:}
Researching transfer learning for fraud prediction at \href{https://www.adyen.com/}{\custombold{Adyen}}.

\end{small}
\vspace{\topsep}

\subsection{Delft University of \newline Technology}
\descript{BSc Computer Science and Eng.}
\location{2015 - 2018 | Delft, NL}
\vspace{\topsep}
\begin{tightemize}
    \item Graduated cum laude with honours
    \item Studied abroad at the National University of Singapore
    \item 8.6/10 final GPA; 9.0/10 BSc thesis
\end{tightemize}

\vspace{0.2\topsep}
Coursework:
\begin{small}
\vspace{0.2\topsep}

\custombold{Intelligence Systems:}
Logic-Based Artificial Intelligence \textbullet \
Multi-Agent Systems Project \textbullet \
Signal + Image Processing \textbullet \
Multimedia Analysis (CM) \textbullet \
Machine Learning \textbullet \
Natural Language Processing
\vspace{0.3\topsep}

\custombold{Computer Systems:}
Computer Organization (TA, CM) \textbullet \
Computer Networks
\vspace{0.3\topsep}

\custombold{Information Systems:}
Web \& Database Technology (CM) \textbullet \
Information \& Data Modeling \textbullet \
Computer Security
\vspace{0.3\topsep}

\custombold{Software Development:}
Object Oriented Programming + Project \textbullet \
Algorithms \& Data Structures (CM) \textbullet \
Software Quality \& Testing \textbullet \
Software Engineering Methods \textbullet \
Concept of Programming Languages \textbullet \
Contextproject
\vspace{0.3\topsep}

\custombold{Fundamentals:}
Reasoning and Logic (CM) \textbullet \
Algorithm Design \textbullet \
Automata, Languages \& Computability \textbullet \
Optimization Algorithms
\vspace{0.3\topsep}

\custombold{Math \& Modeling:}
Computer Graphics \textbullet \
Calculus (CM) \textbullet \
Linear Algebra (TA, CM) \textbullet \
Probability Theory \& Statistics
\vspace{0.3\topsep}

(TA) = Teaching Assistant \\
(CM) = created free Course Materials

\end{small}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github: \href{https://github.com/leonoverweel}{\custombold{/leonoverweel}} \\
Twitter: \href{https://twitter.com/layon_overwhale}{\custombold{@layon\_overwhale}} \\
LinkedIn: \href{https://www.linkedin.com/in/leonoverweel}{\custombold{/leonoverweel}} \\
Full CV: \href{https://leonoverweel.github.io/resume/}{\custombold{leonoverweel.github.io/resume}} \\
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Industry and Research Experience}

\runsubsection{Adyen}
\descript{| MSc Thesis Intern (Machine Learning) }
\location{May 2019 – August 2019 | Amsterdam, NL}
\vspace{\topsep}
\begin{tightemize}
    \item Interning at \href{https://adyen.com}{Adyen} for my MSc thesis, doing a research project on using transfer learning to reuse credit card fraud prediction models between large and small merchants on their payments platform.
\end{tightemize}
\vspace{0.5\topsep}

\runsubsection{ING Bank}
\descript{| BSc Thesis Intern (Software Engineering) }
\location{April 2018 – July 2018 | Amsterdam, NL}
%\vspace{\topsep}
\begin{tightemize}
    \item Worked in a four-student team to create Mapp, an internal tool for customer journey mapping at \href{https://www.ing.com/}{\custombold{ING}}, as our BSc graduation project.
    \item Focused on finding product-market fit by shipping the Java + Polymer web app in two-week sprints and getting user feedback constantly.
    \item Users love Mapp and ING is deploying it throughout the company.
\end{tightemize}
\vspace{0.5\topsep}

\runsubsection{@Large Research}
\descript{| OpenDC Product Lead; Student Researcher }
\location{June 2016 – July 2018 | Delft, NL}
\begin{tightemize}
    \item Worked in the \href{https://atlarge-research.com/}{\custombold{@Large Research}} group to build \href{https://opendc.org}{\custombold{OpenDC}}: a free, open-source datacenter simulator for research and university-level education.
    \item Leadership resp's: sprint planning, conference talks, and teaching classes.
    \item Engineering resp's: database + API design and Python web server development.
    % \item Post-Product Lead, I ran a nine-month study of cloud provider availability.
\end{tightemize}
\vspace{0.5\topsep}

%\runsubsection{Mugsy}
%\descript{| Software Engineering Intern }
%\location{May 2015 – July 2015 | New York, NY}
%\begin{tightemize}
%    \item Full stack developed the %\href{http://mugsy.tv/}{\custombold{Mugsy website}} with a custom CMS to add, edit, and remove multiple types of content pages.
%\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\href{https://dynamicallytyped.com}{\custombold{Dynamically Typed}} (2019): Bi-weekly email newsletter on productized artificial intelligence and machine learning research, with 80+ subscribers.

\vspace{0.3\topsep}
\href{https://weekly.cool}{\custombold{Weekly.Cool}} (2019): Subscription service for weekly email digests for subreddits.

\vspace{0.3\topsep}
\href{https://leonoverweel.com/projects/2019/rl-coursework/}{\custombold{Reinforcement Learning Soccer Bots}} (2019): Implemented and tuned eight different RL algorithms, including deep Q-learning, in a simple soccer game environment.

\vspace{0.3\topsep}
\href{https://leonoverweel.com/projects/2019/mlp-textworld-lstm-dqn/}{\custombold{Reinforcement Learning for Text-Based Games}} (2019): Experimented with techniques to encourage exploration for an RL agent trained to play text-based games.

\vspace{0.3\topsep}
\href{https://leonoverweel.com/projects/2019/nlu-coursework/}{\custombold{Neural Machine Translation with Lexical Model}} (2018): Analyzed a neural machine translation architecture, and implemented and evaluated a lexical model on top of it.

\vspace{0.3\topsep}
\href{https://leonoverweel.com/projects/2018/mlp-1-emnist-learning-and-regularization/}{\custombold{Convolutional Neural Networks Exploration (part 1}}, \href{https://leonoverweel.com/projects/2018/mlp-2-emnist-architectures/}{\custombold{part 2)}} (2018): Implemented different components and training schemes of CNNs and experimented with them on the EMNIST handwritten character recognition task.

\vspace{0.3\topsep}
\href{https://leonoverweel.com/projects/2018/ringvaart/}{\custombold{Keihard voor Kika}} (2018): Formed a crew with three friends, learned to row, and rowed a 100km race in June, raising money for child cancer research.

\vspace{0.3\topsep}
\href{https://leonoverweel.com/projects/2017/hackdelft/}{\custombold{HackDelft}} (2017): Co-founded and organized HackDelft '17, TU Delft's hackathon.

\vspace{0.2cm}
You can see 30+ past projects on \href{http://leonoverweel.com/}{\custombold{leonoverweel.com},} ranging from websites and machine learning projects to videos and hackathons.

\vspace{0.3\topsep}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}

Each skill links to projects for which I've used it; ordered by number of projects.

\vspace{0.3\topsep}
\custombold{Programming Languages:} 
\href{https://leonoverweel.com/tags/language-python/}{\custombold{Python}} \textbullet \
\href{https://leonoverweel.com/tags/language-css/}{\custombold{CSS}} \textbullet \
\href{https://leonoverweel.com/tags/language-html/}{\custombold{HTML}} \textbullet \
\href{https://leonoverweel.com/tags/language-javascript/}{\custombold{JavaScript}} \textbullet \
\href{https://leonoverweel.com/tags/language-c++/}{\custombold{C++}} \textbullet \
\href{https://leonoverweel.com/tags/language-java/}{\custombold{Java}}

\vspace{0.3\topsep}
\custombold{Technical Tools:}
\href{https://leonoverweel.com/tags/tool-git/}{\custombold{Git}} \textbullet \
\href{https://leonoverweel.com/tags/tool-github/}{\custombold{GitHub}} \textbullet \
\href{https://leonoverweel.com/tags/tool-google-app-engine/}{\custombold{Google App Engine}} \textbullet \
\href{https://leonoverweel.com/tags/tool-flask/}{\custombold{Flask}} \textbullet \
\href{https://leonoverweel.com/tags/tool-github-pages/}{\custombold{GitHub Pages}}

\vspace{0.3\topsep}
\custombold{ML Packages:}
\href{https://leonoverweel.com/tags/ml-numpy/}{\custombold{NumPy}} \textbullet \
\href{https://leonoverweel.com/tags/ml-matplotlib/}{\custombold{Matplotlib}} \textbullet \
\href{https://leonoverweel.com/tags/ml-pytorch/}{\custombold{PyTorch}} \textbullet \
\href{https://leonoverweel.com/tags/ml-plotly/}{\custombold{Plotly}} \textbullet \
\href{https://leonoverweel.com/tags/ml-scipy/}{\custombold{SciPy}}

\vspace{0.3\topsep}
\custombold{ML Models:}
\href{https://leonoverweel.com/tags/model-convolutional-neural-network/}{\custombold{Conv. Network}} \textbullet \
\href{https://leonoverweel.com/tags/model-deep-q-network/}{\custombold{Deep Q Network}} \textbullet \
\href{https://leonoverweel.com/tags/model-long-short-term-memory/}{\custombold{Long Short Term Memory}}
\vspace{0.3\topsep}

% \vspace{-\topsep}
% \settowidth\tymin{\custombold{Some experience}}
% \begin{tabulary}{\linewidth}{LLL}
%     & \custombold{Languages} & \custombold{Platforms + Tools} \\
%     \hline
%     \custombold{Working knowledge} & Python, Java, JavaScript, SQL & Numpy, scikit-learn, Compute Engine, App Engine, serverless, Flask, Polymer, OpenAPI, Linux, Docker, Git, GitHub, IntelliJ, PyCharm \\
%     \hline
%     \custombold{Some experience} & C++, Matlab, Assembly, Prolog & nginx, Java Spark, RobotOS, Mindstorms NXT, Visual Studio
% \end{tabulary} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\hspace{-0.3cm}
\begin{tabular}{lll}
2017 - 19 (NL)   & T500: Most Talented Under-26s  & The Next Web\\
2015 (NL)   & 1st Place: The Overall Best WPH Idea      & World Port Hackathon\\
2015 (CA)   & 3rd Place: Google API Prize               & Hack the North\\
\end{tabular}
\vspace{0.1\topsep}

\end{minipage} 
\end{document}
